---
title: "Keeping up with IDS: Week 03 (Alex's slides)"
subtitle: "<br><br> Introduction to Data Science"
author: "[idsed.digital](https://idsed.digital/)"
date: "<br> Alex Homer"
output:
  xaringan::moon_reader:
    css: ["./xaringan-themer.css", "./slides.css"]
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightLines: true
      highlightStyle: solarized-light
      countIncrementalSlides: false
---

```{r child = "../../setup.Rmd"}
```

```{r packages, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emo)
# knitr::opts_chunk$set(dev = "ragg_png")
#Necessary when knitting on Windows, requires `ragg` package
```

class: middle

# .hand[Personal access tokens]


---

## .hand[Personal access tokens]

.hand[
- It seems like RStudio is having some trouble with remembering PATs between sessions
- Two solutions:
  - Create a new one each time
  - Store it in a password manager
- .pink[*Do not* store it in plaintext!]
]
---
class: middle

# .hand[Scaling graphs]


---

## .hand[Scaling graphs]

```{r tribble}
dat <- tribble(
   ~x,   ~y,
   1,    0.5,
   1.5,  1,
   2,    2,
   2.5,  2.5,
   3,    3,
   3.5,  3,
   4,    45,
   4.5,  4.5,
   5,    4,
   5.5,  5,
   6,    5.5
)
```
---

## .hand[Scaling graphs]

```{r first-ggplot}
dat %>% ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```

---

## .hand[Scaling graphs]

```{r first-ggplot-rep, echo = FALSE}
dat %>% ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```
.hand[Hard to see what's going on with the low values!  We might]
.hand[want to crop out the point at] $(4, 45)$.hand[.]

---
## .hand[Scaling graphs:] `filter`

```{r ggplot-filter}
dat %>% filter(y <= 50) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(caption = "Point at x = 4, y = 45 not shown.")
```

---

## .hand[Scaling graphs]

```{r first-ggplot-rep-2, echo = FALSE}
dat %>% ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm")
```
.hand[All the values, including the regression line, are between]
$0$ .hand[and] $15$.hand[.]


---

## .hand[Scaling graphs:] `scale_y_continuous`

```{r ggplot-scale, fig.show = "hide"}
dat %>% ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_y_continuous(limits = c(0, 20)) +
  labs(caption = "Point at x = 4, y = 40 not shown.")
```

---

## .hand[Scaling graphs:] `scale_y_continuous`

```{r ggplot-scale-plot, warning = FALSE}
dat %>% ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_y_continuous(limits = c(0, 20)) +
  labs(caption = "Point at x = 4, y = 0 not shown.")
```

---

## .hand[Scaling graphs:] `coord_cartesian`

```{r ggplot-cartesian}
dat %>% ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  coord_cartesian(ylim = c(0, 20)) +
  labs(caption = "Point at x = 4, y = 100 not shown.")
```

